---
title: "week 03 coding challenge"
author: "."
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```


```{r load libraries}

```


```{r load data}

```

We want to explore whether higher risk of depression increases alcohol consumtion. 

Based on the Latino Health Survey codebook, the four items of depression (PTSD-4; page 6) need to be reversed.

Your task is to manipulate your data using the `tidyverse`'s `mutate`, `case_when` functions and run a series of logistic regression analyses. Use Google search as needed.

Challenge 1: mutate new variables: 
- `ptsd_mean` (average of four ptsd items)
- `ptsd_mean_rev` (reverse of the `ptsd_mean` variable; hint: 6- value)
- `ptsd_mean_rev_std` (standardized value of `ptsd_mean`)
- `audit_c` (participants who responded 1 or 2 ~ 1; else ~0)

For your reference: (pg 8 of the codebook)
How often did you have a drink containing alcohol in the past year? 
1. Four or more times a week <-- coded as '1' 
2. Two to three times per week <-- coded as '1'
3. Two to four times a month <-- coded as '0'
4. Monthly or less <- coded as '0'
5. Never <- coded as '0'

```{r data wrangling}

```


#Now we will be running several logistic regression and compare the results:

Run logistic regression using `ptsd_mean_rev` adjusting for age, sex, and education; use `tidy` function for output; exponent your results and interpret your result using odds ratio
```{r logistic regression 1}

```

Interpretation: 
[ ]

Use `ggfortify`'s `autoplot` function to do model diagnostics
```{r}

```

Explain diagnostic plots:
[ ]



Run logistic regression using `ptsd_mean_rev_std` adjusting for age, sex, and education; use `tidy` function for output; use `divide-by-four` approach and interpret your result using probability scale. 
```{r}

```
Interpretation
[ ]



#Next, visualization
Use `ggplot` to duplicate the figure
Using the `ptsd_mean_rev` variable you created before, you would need to categorize the mean value into four categories: 
if ptsd_mean_rev is :
1-1.9 ~ 1 ; 
2-2.9 ~2; 
3-3.9 ~ 3; 
4+ ~ 4. 

Refer to Healy's book or Google search as a guide. 

```{r visualization}

```

